---
title: "Project03 additional Visualization"
author: "Mohamed Elmoudni"
date: "Monday, March 30, 2015"
output: html_document
---


```{r}
require(ggplot2)
library(ggplot2)
library(plot3D)
library(scatterplot3d)

```

 I took the summary table that Honey, Vuthy, James, and Sonya had created and added few graphics as well

 Please note that i only took the summary with the below following columns:
Category.Nominations,
Count,
Category.Winners,
Count

 Also, I loaded and shared the table as csv using dropconvas website as per below 

```{r}

data1<- read.table(file= "http://dropcanvas.com/dcm0h/1", header = TRUE, sep=",")
str(data1)
head(data1)


```


# Distribution Nominations By Category

```{r, echo=FALSE}

p<- qplot(Category.Nominations, Count,  data= data1, color =Category.Nominations,  size=I(5),
           main = " Distribution Nominations By Category",
           xlab = " Category Nominations ", 
           ylab = " Nomination Count " )   

p + theme_bw()
p


```

# Distribution of Winning By Category

```{r, echo=FALSE}


p<- qplot(Category.Winners, Count.1,  data= data1, color =Category.Winners,  size=I(5),
          main = " Distribution of Winning By Category ",
          xlab = " Winning Category ", 
          ylab = " Winning Count " )   

p + theme_bw()
p

```

# Distribution of Wins over Winning by Nominations Category

```{r}
attach(data1) 
scatterplot3d(Category.Nominations, Category.Winners, Count.1, pch=16, highlight.3d=TRUE,
               type="h", main="Distribution of Wins over Winning by Nominations Category",
               xlab = "Category.Nominations", ylab = "Winning Category", zlab = " Winners")

```




